### 2021-04-17 submission/manuscript.Rmd
Fig 5 caption draft

\includegraphics{figure_5.pdf}
\newpage
\includegraphics{figure_5_16S.pdf}
**Figure 5. 1-day PEG treatment post C. difficile challenge prolongs colonization regardless of whether an FMT is also administered.** A. 
\newpage

>>>>

\includegraphics{figure_5.pdf}
A. Experimental timeline for groups receiving PEG treatment post clindamycin gavage. B. Median and individual CFU/g of C. difficile measured over time via culture. Asterisks indicate time points with significant differences between groups using Kruskall-Wallis tests with a Benjamini-Hochberg correction. Limit of detection is 1e2 CFU/g. Background shading indicates PEG treatment period for applicable groups. Opacity of points reflects time point. C. Median and individual Shannon Diversity measured over time. Asterisks, background shading, and opacity of points consistent with (B). D. Median and individual richness measured over time. Asterisks, background shading, and opacity of points consistent with (B).

\newpage
\includegraphics{figure_5_16S.pdf}
**Figure 5. 1-day PEG treatment post C. difficile challenge prolongs colonization regardless of whether an FMT is also administered.** A. PCoA of all groups + FMT plotted over time. Opacity of points reflects time point. B. Relative abundance of genera significantly different over multiple time points post FMT or PBS treatment, plotted over time. Limit of detection is .1%. C. Relative abundances of top 6 significant genera ranked by number of days significant, plotted over time. Limit of detection is .1%.
